INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-03-14 paper/paper.tex
adjust figsizes

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_loc_svals_left.pdf}
  \caption{Singular valus left}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_loc_svals_inner.pdf}
  \caption{Singular valus inner}\label{fig:loc_svals_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{./figures/beam/fig_loc_svals_right.pdf}
  \caption{Singular valus right}\label{fig:loc_svals_right}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_left_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_left_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_inner_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_inner_hapod}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_right_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_right_hapod}
\endminipage
\end{figure}

\begin{table}
    \caption{HAPOD inner}\label{tab:hapod_inner}
    \input{./src/beam/tables/hapod_inner.tex}
\end{table}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_left_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_left_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_inner_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_inner_heuristic}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{./figures/beam/fig_proj_error_right_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_right_heuristic}
\endminipage
\end{figure}

\begin{table}
    \caption{Heuristic rrf inner}\label{tab:heuristic_inner}
    \input{./src/beam/tables/heuristic_inner.tex}
\end{table}

@@

\begin{figure}[!htb]
    \includegraphics[width=\linewidth]{./figures/beam/fig_loc_rom_error.pdf}
    \caption{A really Awesome Image}\label{fig:loc_rom_error}
\end{figure}

>>>>

\makeatletter
orig: \f@size
\verb+\normalsize+ \normalsize \f@size
\makeatother
It seems that the font size is actually set to 11pt, although 12pt should be used in the body of the text.

@@

\begin{figure}[!htb]
\minipage{0.49\textwidth}
  \includegraphics[]{./figures/beam/fig_loc_svals_left.pdf}
  \caption{Singular valus left}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.49\textwidth}
  \includegraphics[]{./figures/beam/fig_loc_svals_right.pdf}
  \caption{Singular valus right}\label{fig:loc_svals_right}
\endminipage\hfill\\%
\begin{center}
\minipage{0.49\textwidth}
  \includegraphics[]{./figures/beam/fig_loc_svals_inner.pdf}
  \caption{Singular valus inner}\label{fig:loc_svals_inner}
\endminipage
\end{center}
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.49\textwidth}
  \includegraphics{./figures/beam/fig_proj_error_left_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_left_hapod}
\endminipage\hfill
\minipage{0.49\textwidth}
  \includegraphics{./figures/beam/fig_proj_error_right_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_right_hapod}
\endminipage\hfill\\
\begin{center}
\minipage{0.49\textwidth}%
  \includegraphics{./figures/beam/fig_proj_error_inner_hapod.pdf}
  \caption{Projection error hapod}\label{fig:proj_error_inner_hapod}
\endminipage
\end{center}
\end{figure}

\begin{table}
    \centering
    \caption{HAPOD inner}\label{tab:hapod_inner}
    \input{./src/beam/tables/hapod_inner.tex}
\end{table}

@@

\begin{figure}[!htb]
\minipage{0.49\textwidth}
  \includegraphics{./figures/beam/fig_proj_error_left_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_left_heuristic}
\endminipage\hfill
\minipage{0.49\textwidth}
  \includegraphics{./figures/beam/fig_proj_error_right_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_right_heuristic}
\endminipage\hfill\\
\begin{center}
\minipage{0.49\textwidth}%
  \includegraphics{./figures/beam/fig_proj_error_inner_heuristic.pdf}
  \caption{Projection error }\label{fig:proj_error_inner_heuristic}
\endminipage
\end{center}
\end{figure}

\begin{table}
    \centering
    \caption{Heuristic rrf inner}\label{tab:heuristic_inner}
    \input{./src/beam/tables/heuristic_inner.tex}
\end{table}

@@

\begin{figure}[!htb]
    \centering
    \includegraphics{./figures/beam/fig_loc_rom_error.pdf}
    \caption{Local ROM error relative to FOM.}\label{fig:loc_rom_error}
\end{figure}
